---
title: "lab_report_knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
```{r setup}
library(knapsack)
```
## Introduction

This vignette provides a detailed report on the functionality of the Knapsack package. We will cover three main functions: knapsack_brute_force, knapsack_dynamic, and greedy_knapsack.

## knapsack_brute_force

The knapsack_brute_force function is used to solve the knapsack problem using a brute force approach. It takes a data frame with items' values and weights, and it finds the maximum knapsack value along with the selected items.

### How much time does it take to run the algorithm for n = 16 objects?

```{r}
# Define the number of objects
n <- 16

# Set the random number generator version and seed
RNGversion(min(as.character(getRversion()), "3.5.3"))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")

# Generate data for 16 objects
knapsack_objects <- data.frame(
  w = sample(1:100, size = n, replace = TRUE),  # Adjust the weight range as needed
  v = runif(n, 0, 1000)  # Adjust the value range as needed
)

# Measure the time taken for the algorithm
timing <- system.time({
  result <- brute_force_knapsack(knapsack_objects, W = 200)  # Adjust the knapsack size (W) as needed
})

# Output the result along with the time taken
cat("For n = 16 objects:\n")
cat("Maximum Value:", result$value, "\n")
cat("Selected Elements:", result$elements, "\n")
cat("Time taken:", timing[["elapsed"]], "seconds\n")
```

## knapsack_dynamic

The knapsack_dynamic function provides a dynamic programming solution to the knapsack problem. It efficiently finds the maximum value of items to include in the knapsack under the given weight constraint.

### How much time does it takes to run the algorithm for n = 500 objects?

```{r}
# Define the number of objects
n <- 500

# Set the random number generator version and seed
RNGversion(min(as.character(getRversion()), "3.5.3"))
set.seed(42, kind="Mersenne-Twister", normal.kind="Inversion")

# Generate data for 500 objects
knapsack_objects <- data.frame(
  w=sample(1:100, size=n, replace=TRUE),  # Adjust the weight range as needed
  v=runif(n, 0, 1000)  # Adjust the value range as needed
)

# Measure the time taken for the algorithm
timing_dynamic <- system.time({
  result_dynamic <- knapsack_dynamic(knapsack_objects, W=200)  # Adjust the knapsack size (W) as needed
})

# Output the result along with the time taken
cat("For n = 500 objects:\n")
cat("Maximum Value:", result_dynamic$max_value, "\n")
cat("Selected Items:", result_dynamic$selected_items, "\n")
cat("Time taken:", timing_dynamic[["elapsed"]], "seconds\n")
```

## greedy_knapsack

The greedy_knapsack function uses a greedy heuristic approach to solve the knapsack problem. Although it may not provide an exact result, it offers a fast way to approximate the maximum value.

### How much time does it takes to run the algorithm for n = 1000000 objects?

```{r}
# Define the number of objects
n <- 1000000

# Set the random number generator version and seed
RNGversion(min(as.character(getRversion()), "3.5.3"))
set.seed(42, kind="Mersenne-Twister", normal.kind="Inversion")

# Generate data for 1,000,000 objects
knapsack_objects <- data.frame(
  w=sample(1:100, size=n, replace=TRUE),  # Adjust the weight range as needed
  v=runif(n, 0, 1000)  # Adjust the value range as needed
)

# Measure the time taken for the algorithm
timing_greedy <- system.time({
  result_greedy <- greedy_knapsack(knapsack_objects, W=200)  # Adjust the knapsack size (W) as needed
})

# Output the result along with the time taken
cat("For n = 1,000,000 objects:\n")
cat("Maximum Value:", result_greedy$value, "\n")
cat("Selected Elements:", result_greedy$elements, "\n")
cat("Time taken:", timing_greedy[["elapsed"]], "seconds\n")
```

## Performance Optimization



### What performance gain could you get by trying to improving your code?

### Profiling the Brute Force Knapsack Function

```{r}
library(profvis)

# Profile the brute_force_knapsack function for n = 16 objects
# Define n and generate data for 16 objects
n <- 16

# Set the random number generator version and seed
RNGversion(min(as.character(getRversion()), "3.5.3"))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")

# Generate data for 16 objects
knapsack_objects <- data.frame(
  w = sample(1:100, size = n, replace = TRUE),  # Adjust the weight range as needed
  v = runif(n, 0, 1000)  # Adjust the value range as needed
)

# Profile the brute_force_knapsack function for n = 16 objects
profvis({
  result_brute_force <- brute_force_knapsack(knapsack_objects, W = 200)  # Adjust the knapsack size (W) as needed
})
```

### Profiling the Dynamic Knapsack Function

```{r}
library(profvis)

# Profile the knapsack_dynamic function for n = 500 objects
# Define n and generate data for 500 objects
n <- 500

# Set the random number generator version and seed
RNGversion(min(as.character(getRversion()), "3.5.3"))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")

# Generate data for 500 objects
knapsack_objects <- data.frame(
  w = sample(1:100, size = n, replace = TRUE),  # Adjust the weight range as needed
  v = runif(n, 0, 1000)  # Adjust the value range as needed
)

# Profile the knapsack_dynamic function for n = 500 objects
profvis({
  result_dynamic <- knapsack_dynamic(knapsack_objects, W = 200)  # Adjust the knapsack size (W) as needed
})
```

### Profiling the Greedy Knapsack Function

```{r}
library(profvis)

# Profile the greedy_knapsack function for n = 1,000,000 objects
# Define n and generate data for 1,000,000 objects
n <- 1000000

# Set the random number generator version and seed
RNGversion(min(as.character(getRversion()), "3.5.3"))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")

# Generate data for 1,000,000 objects
knapsack_objects <- data.frame(
  w = sample(1:100, size = n, replace = TRUE),  # Adjust the weight range as needed
  v = runif(n, 0, 1000)  # Adjust the value range as needed
)

# Profile the greedy_knapsack function for n = 1,000,000 objects
profvis({
  result_greedy <- greedy_knapsack(knapsack_objects, W = 200)  # Adjust the knapsack size (W) as needed
})
```

### What performance gain could you get by using Rcpp and C++?

```{r}
library(microbenchmark)
library(Rcpp)
# Function to execute the R implementation
knapsack_brute_force_R <- function(W, weights, values) {
  # ... (existing R code)
}

# Function to execute the Rcpp implementation
sourceCpp("C:/Users/sange/OneDrive/Documents/knapsack/src/knapsack.cpp")  # Assuming the C++ code is in 'knapsack.cpp'

knapsack_brute_force_Rcpp <- function(W, weights, values) {
  knapsack_brute_force(W, weights, values, TRUE)
}

# Define different 'n' values for the number of items
n_values <- c(16, 500, 1000)  # Use appropriate values for benchmarking

results <- lapply(n_values, function(n) {
  # Generate data for the given 'n' value
  weights <- runif(n, 1, 100)
  values <- runif(n, 1, 1000)
  W <- 200  # Adjust the knapsack size as needed
  
  # Execute R version and Rcpp version and capture execution times
  timings <- microbenchmark(
    R_version = knapsack_brute_force_R(W, weights, values),
    Rcpp_version = knapsack_brute_force_Rcpp(W, weights, values),
    times = 100  # Number of iterations to measure performance
  )
  return(timings)
})
```

```{r}
for (i in 1:length(results)) {
  print(paste("For n =", n_values[i]))
  print(summary(results[[i]]))
}
```

## Conclusion

The Knapsack package provides three functions to address the knapsack problem using different approaches. Use these functions to find optimal or approximate solutions based on your needs.


